---
title: "2. Survey Data Processing [do not run]"
---

## Data imports

```{r}
knitr::opts_chunk$set(message = FALSE, warning = FALSE)

source('helpers.R')

pl = read_rename_csv(paste0("pl_survey_post_NEW.csv"), "_post") %>%
  left_join(., read_rename_sav("pl_survey_w1.sav", "_w1"), 
            by = c("respondent_id_post" = "respondent_id_w1")) %>%
  left_join(., read_rename_sav("pl_survey_pre.sav", "_pre"), 
            by = c("respondent_id_post" = "respondent_id_pre")) %>%
  setNames(., tolower(names(.))) %>% 
  mutate(news_self = rowMeans(
    select(., paste0("q8_h2_r", 1:9, "_w1")), na.rm = T)) # BC: ACCORDING TO PAP, THIS SHOULD TAKE INTO ACCOUNT W2

us = read_rename_csv(paste0("us_survey_post_NEW.csv"), "_post") %>%
  left_join(., read_rename_csv("us_survey_all.csv", ""), 
            by = c("person_id_post" = "person_id")) %>%
  setNames(., tolower(names(.))) %>% 
  mutate(news_self = rowMeans(
    select(., 
           paste0("days_week_", c("tv", "print", "radio", 
           "web", "sm", "msg", "f2f", "app", "search"), "_w1")), 
    na.rm = T))
```

Select relevant variables for the American dataset
```{r}
us = select(us, c(
  # respondent information
  "person_id_post", "gender_w0_fac", "age_w0", "edu_w0_fac",
  "party_w3", "ideo_w3", "approve_trump_w1",
  
  # political knowledge
  paste0("know_", 1:5, "_post"),
  paste0("cur_event_0", 1:4, "_post"),
  
  # participation 
  "par_2020_post",
  
  # attitude importance
  paste0("important_", c("gun", "immigrant", "climate", "trump", "econ"), "_w3"),
  paste0("isperso_", 1:5, "_post"),
  
  # attitude strength 
  paste0("strong_", c("gun", "immigrant", "climate", "trump", "econ"), "_w3"),
  paste0("isstrong_", 1:5, "_post"),
  
  # affective polarization: feeling thermometer 
  # democrats, republicans, liberals, conservatives, 
  # gun control, immigration, climate change, economy
  paste0("ft_", c("dem_supporters", "rep_supporters", "liberals", 
                  "conservatives", "gun", "immigrant", 
                  "climate", "econ"), "_w3"),
  paste0("thermom_", c(4:7, 9:12), "_post"),
  
  # affective polarization: negative traits
  # out-partisans, (democrats), out-ideologues, (liberals)
  # gun control, immigration, climate change, economy
  paste0("stupid_", c("party_opp", "ind_dem", "ideo_opp", "ind_cons", 
                      "gun", "immigrant", "climate", "econ"), "_w3"),
  paste0("stupid_", c(7, 9, 1, 2, 3, 5), "_post"),
  
  # affective polarization: understanding
  # out-partisans, out-ideologues
  # gun control, immigration, climate change, economy
  paste0("understand_", c("party_opp", "ideo_opp", 
                          "gun", "immigrant", "climate", "econ"), "_w3"),
  paste0("understand_", c(7, 9, 1, 2, 3, 5), "_post"),
  
  # attribution of malevolence 
  paste0("malvol_", 1:5, "_w3"),
  paste0("malvol_", 1:5, "_post"),
  
  # support for compromise
  paste0("supp_compr_", 1:4, "_w3"), 
  paste0("compromise_", 1:4, "_post"),
  
  # perceived polarization
  paste0("perpol_", 1:4, "_w3"),
  paste0("perpol_", 1:4, "_post"),
  
  # physical well-being
  paste0("well_act_", 1:5, "_post"),
  
  # mental well-being 
  paste0("well_feelings_", 1:6, "_post"),
  
  # exposure variables
  # "visits_raw_w3_post", "visits_u_w3_post", "day_range_w3_post", 
  # "active_days_w3_post", "count_domains_w3_post", 
  # "domain_center_w3_post", "domain_left_w3_post", "domain_right_w3_post", 
  # "domain_center_mean_w3_post", "domain_left_mean_w3_post",
  # "domain_right_mean_w3_post", 
  "news_self", "diet_lean_w2",
  "news_post", "news_ideo_post",
  
  # condition
  "nonews_condition_post",
  
  # attitude variables
  "att_econ_1_w3", "att_econ_2_w3", "att_econ_3_w3", 
  "att_climate_1_w3", "att_climate_2_w3", "att_climate_3_w3", 
  "att_immigrant_1_w3", "att_immigrant_2_w3", "att_immigrant_3_w3", 
  "att_gun_1_w3", "att_gun_2_w3", "att_gun_3_w3"
))
```

Rename columns for the American dataset
```{r}
colnames(us) = c(
  # respondent information
  "person_id", "sex", "age", "edu",
  "party", "ideo", "approve_trump",
  
  # political knowledge
  paste0("know_", 1:5, "_post"),
  paste0("know_fac_", 1:4, "_post"),
  
  # participation 
  "ptc_post",
  
  # attitude importance
  paste0("att_imp_", c("gun", "immigrant", "climate", "trump", "econ"), "_pre"),
  paste0("att_imp_", c("gun", "immigrant", "climate", "trump", "econ"), 
         "_post"),
  
  # attitude strength 
  paste0("att_str_", c("gun", "immigrant", "climate", "trump", "econ"), "_pre"),
  paste0("att_str_", c("gun", "immigrant", "climate", "trump", "econ"), 
         "_post"),
  
  # affective polarization: feeling thermometer 
  # democrats, republicans, liberals, conservatives, 
  # gun control, immigration, climate change, economy
  paste0("ft_", c("dem", "rep", "lib", "cons", "gun", "immigrant", 
                  "climate", "econ"), "_pre"),
  paste0("ft_", c("dem", "rep", "lib", "cons", "gun", "immigrant", 
                  "climate", "econ"), "_post"),
  
  # affective polarization: negative traits
  # out-partisans, (democrats), out-ideologues, (liberals)
  # gun control, immigration, climate change, economy
  paste0("stupid_", c("party_opp", "ind_dem", "ideo_opp", "ind_cons", 
                      "gun", "immigrant", "climate", "econ"), "_pre"),
  paste0("stupid_", c("party_opp", "ideo_opp", 
                      "gun", "immigrant", "climate", "econ"), "_post"),
  
  # affective polarization: understanding
  # out-partisans, out-ideologues
  # gun control, immigration, climate change, economy
  paste0(c("under_party_opp", "under_ideo_opp", "under_gun", 
           "under_immigrant", "under_climate", "under_econ"), "_pre"),
  paste0(c("under_party_opp", "under_ideo_opp", "under_gun", 
           "under_immigrant", "under_climate", "under_econ"), "_post"),
  
  # attribution of malevolence 
  paste0("malvol_", 1:5, "_pre"),
  paste0("malvol_", 1:5, "_post"),
  
  # support for compromise
  paste0("comp_", 1:4, "_pre"), 
  paste0("comp_", 1:4, "_post"),
  
  # perceived polarization
  paste0("perpol_", 1:4, "_pre"),
  paste0("perpol_", 1:4, "_post"),
  
  # physical well-being
  paste0("well_act_", 1:5, "_post"),
  
  # mental well-being 
  paste0("well_feel_", 1:6, "_post"),
  
  # exposure variables
  # "visits_raw", "visits_u", "day_range", "active_days", "count_domains", 
  # "domain_center", "domain_left", "domain_right", 
  # "domain_center_mean", "domain_left_mean", "domain_right_mean",  
  "news_self", "news_ideo_self",
  "news", "news_ideo",
  
  # condition
  "condition",
  
  # attitudes
  "att_econ_1_pre", "att_econ_2_pre", "att_econ_3_pre", 
  "att_climate_1_pre", "att_climate_2_pre", "att_climate_3_pre", 
  "att_immigrant_1_pre", "att_immigrant_2_pre", "att_immigrant_3_pre", 
  "att_gun_1_pre", "att_gun_2_pre", "att_gun_3_pre"
)
```

Select relevant columns for the Polish dataset
```{r}
pl = select(pl, c(
  # respondent information
  "person_id_post", "sex_w1", "age_w1", "edu_w1",
  "q2dwa_r1_w1", "qq2dwa_r1_pre", "q2_r1_w1",
  "qq2_r1_pre", "q4pref_w1", "q4niepref_w1", 
  "qq4pref_pre", "qq4niepref_pre",
  
  # political knowledge
  paste0("exp6know_r", 1:5, "_post"),
  paste0("exp9wiedza", 1:4, "_post"),
  
  # participation 
  paste0("exp24particip_r", 1:8, "_post"),
  
  # attitude importance
  paste0("qq40_r", c(1:3, 5:6), "_pre"),
  paste0("exp11qq40_r", c(1:3, 5:6), "_post"),
  
  # attitude strength 
  paste0("qq39_r", c(1:3, 5:6), "_pre"),
  paste0("exp10qq39_r", c(1:3, 5:6), "_post"),
  
  # affective polarization: feeling thermometer
  # out-partisans (farthest from, PIS, SLD)
  # people with leftist views, people with rightist views, 
  # women's rights, religion, EU, economy
  paste0("qq50r", c(1,4:11) ,"_pre"),
  paste0("exp16qq50r", c(1,4:11) ,"_post"),
  
  # affective polarization: negative traits
  # out-partisans farthest from
  # women's rights, religion, EU, economy
  # PROBLEM: OUT-IDEOLOGUES PIS & SLD ARE MISSING
  "qq55c_h1_r1_pre", "qq53_1_h1_r1_pre", "qq52_2_h1_r1_pre", 
  "qq53_2_h1_r1_pre", "qq52_1_h1_r1_pre",
  
  # out-partisans (farthest from, PIS, SLD)
  # people with leftist views, people with rightist views, 
  # women's rights, religion, EU, economy
  paste0("exp15p08_h1_r", c(1,5:12), "_post"),
  
  # affective polarization: understanding
  # out-partisans (farthest from, PIS, SLD)
  # people with leftist views, people with rightist views, 
  # women's rights, religion, EU, economy
  paste0("qq47_h1_r", c(2,5:12), "_pre"),
  paste0("exp14qq47_h1_r", c(2,5:12), "_post"),
  
  # attribution of malevolence 
  paste0("qq58zw_1_r", 2:6, "_pre"),
  paste0("qq58op_1_r", 2:6, "_pre"),
  paste0("exp21qq58zw_1_r", 2:6, "_post"),
  paste0("exp22qq58op_1_r", 2:6, "_post"),
  
  # support for compromise
  paste0("compromise", 1:4, "_r1_pre"),
  paste0("exp", 17:20, "compromise", 1:4, "_r1_post"),
  
  # perceived polarization
  paste0("qq58_2_r", 2:5, "_pre"),
  paste0("exp23qq58_2_r", 2:5, "_post"),
  
  # physical well-being
  paste0("exp5_r", 1:5, "_post"),

  # mental well-being 
  paste0("exp4_r", 1:6, "_post"),
  
  # exposure variables
  # "visits_raw_w2_post", "visits_u_w2_post", "day_range_w2_post", 
  # "active_days_w2_post", "count_domains_w2_post", 
  # "domain_center_w2_post", "domain_left_w2_post", "domain_right_w2_post", 
  # "domain_center_mean_w2_post", "domain_left_mean_w2_post",
  # "domain_right_mean_w2_post", 
  "news_self", "f1_pre",
  "news_post", "news_ideo_post",
  
  # condition
  "wave2kontrolna_pre", "wave2eksperymentalna_pre",
  
  # attitudes
  "v2q24_1_r1_pre", "v2q24_2_r1_pre", "v2q24_3_r1_pre", 
  "v2q25_1_r1_pre", "v2q25_2_r1_pre", "v2q25_3_r1_pre", 
  "v2q27_1_r1_pre", "v2q27_2_r1_pre", "v2q27_3_r1_pre", 
  "v2q28_1_r1_pre", "v2q28_2_r1_pre", "v2q28_3_r1_pre"
))
```

Rename columns for the Polish dataset
```{r}
colnames(pl) = c(
  # respondent information
  "person_id", "sex", "age", "edu",
  "suppgov1", "suppgov2", "ideo1",
  "ideo2", "party1", "opp_party1", 
  "party2", "opp_party2",
  
  # political knowledge
  paste0("know_", 1:5, "_post"),
  paste0("know_fac_", 1:4, "_post"),
  
  # participation 
  paste0("ptc_", 1:8, "_post"),
  
  
  # attitude importance
  paste0("att_imp_", 1:5, "_pre"),
  paste0("att_imp_", 1:5, "_post"),
  
  # attitude strength 
  paste0("att_str_", 1:5, "_pre"),
  paste0("att_str_", 1:5, "_post"),
  
  # affective polarization: feeling thermometer
  # out-partisans (farthest from, PIS, SLD)
  # people with leftist views, people with rightist views, 
  # women's rights, religion, EU, economy
  paste0("ft_", c("far", "pis", "sld", "lw", "rw", 
                  "women", "rel", "eu", "econ"),"_pre"),
  paste0("ft_", c("far", "pis", "sld", "lw", "rw", 
                  "women", "rel", "eu", "econ"),"_post"),
  
  # affective polarization: negative traits
  # out-partisans farthest from
  # women's rights, religion, EU, economy
  # PROBLEM: OUT-IDEOLOGUES PIS & SLD ARE MISSING
  "stupid_far_pre", "stupid_women_pre", "stupid_rel_pre", 
  "stupid_eu_pre", "stupid_econ_pre",
  
  # out-partisans (farthest from, PIS, SLD)
  # people with leftist views, people with rightist views, 
  # women's rights, religion, EU, economy
  paste0("stupid_", c("far", "pis", "sld", "lw", "rw", 
                      "women", "rel", "eu", "econ"),"_post"),
  
  # affective polarization: understanding
  # out-partisans (farthest from, PIS, SLD)
  # people with leftist views, people with rightist views, 
  # women's rights, religion, EU, economy
  paste0("under_", c("far", "pis", "sld", "lw", "rw", 
                     "women", "rel", "eu", "econ"), "_pre"),
  paste0("under_", c("far", "pis", "sld", "lw", "rw", 
                     "women", "rel", "eu", "econ"), "_post"),
  
  # attribution of malevolence 
  paste0("malvol_gov_", 1:5, "_pre"),
  paste0("malvol_op_", 1:5, "_pre"),
  paste0("malvol_gov_", 1:5, "_post"),
  paste0("malvol_op_", 1:5, "_post"),
  
  # support for compromise
  paste0("comp_", 1:4, "_pre"),
  paste0("comp_", 1:4, "_post"),
  
  # perceived polarization
  paste0("perpol_", 1:4, "_pre"),
  paste0("perpol_", 1:4, "_post"),
  
  # physical well-being
  paste0("well_act_", 1:5, "_post"),

  # mental well-being 
  paste0("well_feel_", 1:6, "_post"),
  
  # exposure variables
  # "visits_raw", "visits_u", "day_range", "active_days", "count_domains", 
  # "domain_center", "domain_left", "domain_right", 
  # "domain_center_mean", "domain_left_mean", "domain_right_mean",  
  "news_self", "news_like_self",
  "news", "news_ideo",
  
  # condition
  "condition_control", "condition_experimental",
  
  # attitudes
    "att_econ_1_pre", "att_econ_2_pre", "att_econ_3_pre",
  "att_women_1_pre", "att_women_2_pre", "att_women_3_pre",
  "att_relig_1_pre", "att_relig_2_pre", "att_relig_3_pre",
  "att_eu_1_pre", "att_eu_2_pre", "att_eu_3_pre"
)
```

## Demographic variables

Sex
```{r}
# POLAND
pl$sex = dplyr::recode(pl$sex, `1` = "Male", `2` = "Female")
```

Age (categorical variable)
```{r}
# UNITED STATES
us$age = case_when(
  us$age %in% 0:17 ~ "Age: 0–17",
  us$age %in% 18:24 ~ "Age: 18–24",
  us$age %in% 25:34 ~ "Age: 25–34",
  us$age %in% 35:44 ~ "Age: 35–44",
  us$age %in% 45:54 ~ "Age: 45–54",
  us$age %in% 55:200 ~ "Age: 55+")

pl$age = case_when(
  pl$age %in% 2 ~ "Age: 18–24",
  pl$age %in% 3 ~  "Age: 25–34",
  pl$age %in% 4 ~ "Age: 35–44",
  pl$age %in% 5 ~  "Age: 45–54",
  pl$age %in% 6 ~ "Age: 55+")
```

Educational attainment 
```{r}
# UNITED STATES
us$edu = 
  dplyr::recode(us$edu,
    `Associate Degree` = "Education: Junior college", 
    `College Degree (such as B.A., B.S.)` = "Education: Bachelor", 
    `High school graduate` = "Education: High school", 
    `Master's degree` = "Education: Graduate school", 
    `Completed some college, but no degree` = "Education: Junior college", 
    `Completed some graduate, but no degree` = "Education: Bachelor", 
    `Doctorate degree` = "Education: Graduate school", 
    `Other post-high school vocational training` = "Education: High school", 
    `Middle School - Grades 4-8` = "Education: Less than high school", 
    `Completed some high school` = "Education: Less than high school"
  )

# POLAND
pl$edu = case_when(
  pl$edu %in% 1 ~ "Education: Less than high school",
  pl$edu %in% 2 ~ "Education: Vocational degree",
  pl$edu %in% 3 ~  "Education: High school",
  pl$edu %in% 4 ~ "Education: Some college",
  pl$edu %in% 5 ~  "Education: Bachelor degree",
  pl$edu %in% 6 ~ "Education: Graduate school")
```

## Independent variables 

Experimental condition
```{r}
# UNITED STATES
us$condition = dplyr::recode(us$condition, 
                      `control` = "No News - Control",
                      `experiment` = "No News - Experiment")

# POLAND
pl$condition = ""
pl$condition[!is.na(pl$condition_control)] = "More News - Control"
pl$condition[!is.na(pl$condition_experimental)] = "More News - Experiment"
```

Partisanship (used to identify political out-groups) 
```{r}

# left-right attitude index
us <- us %>%
  mutate(
    leftright_att = select(., c(
      att_econ_1_pre, att_econ_2_pre, att_econ_3_pre, 
      att_climate_1_pre,  att_climate_2_pre, att_climate_3_pre, 
      att_immigrant_1_pre, att_immigrant_2_pre, att_immigrant_3_pre, 
      att_gun_1_pre, att_gun_2_pre, att_gun_3_pre)) %>%
      rowMeans(na.rm = TRUE))

# UNITED STATES
us$party_bin = case_when(
  us$party %in% 1:3 ~ "Democrat", 
  us$party %in% 4 ~ "Independent", 
  us$party %in% 5:7 ~ "Republican")

# Impute using ideology
us$party_bin[(us$party_bin == "Independent" | is.na(us$party_bin)) & us$ideo < 5] = "Democrat" 
us$party_bin[(us$party_bin == "Independent" | is.na(us$party_bin)) & us$ideo > 5] = "Republican" 

# Impute using support for Trump
us$party_bin[(us$party_bin == "Independent" | is.na(us$party_bin))& us$approve_trump < 5] = "Democrat" 
us$party_bin[(us$party_bin == "Independent" | is.na(us$party_bin)) & 
             us$approve_trump > 5] = "Republican" 

# Assign remaining randomly - OLD
# us$party_bin[us$party_bin == "Independent"] = 
#   sample(c("Democrat", "Republican"), size = 1)

# Impute using left-right attitude index
us$party_bin[(us$party_bin == "Independent" | is.na(us$party_bin)) & us$leftright_att < 7] = "Democrat" 
us$party_bin[(us$party_bin == "Independent" | is.na(us$party_bin)) & us$leftright_att > 7] = "Republican" 

# POLAND

pl <- pl %>%
  mutate(
    leftright_att = select(., c(
      "att_econ_1_pre", "att_econ_2_pre", "att_econ_3_pre",
  "att_women_1_pre", "att_women_2_pre", "att_women_3_pre",
  "att_relig_1_pre", "att_relig_2_pre", "att_relig_3_pre",
  "att_eu_1_pre", "att_eu_2_pre", "att_eu_3_pre")) %>%
      rowMeans(na.rm = TRUE))

pl$party_bin = "missing"

# Opponents vs. proponents government
pl$party_bin[pl$suppgov1<5] = "Anti"
pl$party_bin[pl$suppgov1>5] = "Pro"

pl$party_bin[pl$party_bin == "missing" & pl$suppgov2<5] = "Anti"
pl$party_bin[pl$party_bin == "missing" & pl$suppgov2>5] = "Pro"

# Impute using ideology 
pl$party_bin[pl$party_bin == "missing" & pl$ideo1<5] = "Anti"
pl$party_bin[pl$party_bin == "missing" & pl$ideo1>5] = "Pro"

pl$party_bin[pl$party_bin == "missing" & pl$ideo2<5] = "Anti"
pl$party_bin[pl$party_bin == "missing" & pl$ideo2>5] = "Pro"

# Impute using party  
pl$party_bin[pl$party_bin == "missing" & pl$party1 == 1] = "Pro"
pl$party_bin[pl$party_bin == "missing" & pl$opp_party1 == 1] = "Anti"

pl$party_bin[pl$party_bin == "missing" & pl$party2 == 1] = "Pro"
pl$party_bin[pl$party_bin == "missing" & pl$opp_party2 == 1] = "Anti"

# Randomly impute remaining 17 independents - OLD
# pl$party_bin[pl$party_bin == "missing"] = 
#   sample(c("Pro", "Anti"), size = 1)

pl$party_bin[pl$party_bin == "missing" & pl$leftright_att < 6] = "Anti"
pl$party_bin[pl$party_bin == "missing" & pl$leftright_att > 6] = "Pro"
```

Partisan identity strength
```{r}
# UNITED STATES
us$party_strength <- abs(us$party - 4)

# POLAND
pl$party_strength <- abs(pl$suppgov1 - 5)
```

News exposure and congenial news exposure
```{r}

# this is wrong and not needed
# UNITED STATES
# us$news = us$count_domains / us$active_days
# us$news_like = us$domain_left / us$active_days
# us$news_like[which(us$party_bin == "Democrat")] = 
#   us$domain_left[which(us$party_bin == "Democrat")] / 
#   us$active_days[which(us$party_bin == "Democrat")]
# 
# # POLAND
# pl$news = pl$count_domains / pl$active_days
# pl$news_like = pl$domain_left / pl$active_days
# pl$news_like[which(pl$party_bin == "Pro")] = 
#   pl$domain_left[which(pl$party_bin == "Pro")] / 
#   pl$active_days[which(pl$party_bin == "Pro")]

# flip news ideology for Democrats
us <- us %>%
  mutate(news_like = ifelse(
    party_bin == "Democrat", news_ideo*(-1), news_ideo))

# also for self-reported exposure
us <- us %>%
  mutate(news_like_self = ifelse(
    party_bin == "Democrat", news_ideo_self*(-1), news_ideo_self))

# flip news ideology for those with anti-government position
pl <- pl %>%
  mutate(news_like = ifelse(
    party_bin == "Anti", news_ideo*(-1), news_ideo))

# also for self-reported exposure
pl <- pl %>%
  mutate(news_like_self_r = ifelse(
    party_bin == "Anti", news_like_self*(-1), news_like_self))

```


## Dependent variables

> Political knowledge

**United States** and **Poland** [only in post-survey]

  1. Self-perceived knowledge
  
    - I know pretty much about politics.
    - I do not feel very knowledgeable about politics. (-)
    - Among my circle of friends, I'm one of the “experts” on politics.
    - Compared to most other people, I know less about politics. (-)
    - When it comes to politics, I really don't know a lot (-)
  
  2. Factual knowledge (questions change every week)
  
```{r}
# UNITED STATES 

# invert negatively coded items
for (i in c(2,4,5)){us[,paste0("know_", i, "_post")] = 
  invert(us[,paste0("know_", i, "_post")])}

# correct incorrect dummy for knowledge questions
for (i in 1:4){
  us[,paste0("know_fac_",i, "_post")] = 
    dplyr::recode(us[,paste0("know_fac_",i, "_post")], 
           `1` = 1, `2` = 0, `3` = 0, `4` = 0, .default = 0)
}

# calculate row means and totals
us$know_post = rowMeans(select(us,paste0("know_", c(1:5), "_post")), na.rm = T)
us$know_fac_post = rowSums(select(us,paste0("know_fac_", c(1:4), "_post")), 
                           na.rm = T)

# POLAND 

# invert negatively coded items 
for (i in c(2,4,5)){ pl[,paste0("know_", i, "_post")] = 
  invert(pl[,paste0("know_", i, "_post")])}

# correct incorrect dummy for knowledge questions
for (i in 1:4){
  correct = c(3, 1, 3, 1)[i]
  incorrect = c(1:4)[1:4 %notin% correct]
  
  pl[,paste0("know_fac_",i, "_post")] = 
    case_when(
      pl[,paste0("know_fac_",i, "_post")] %in% correct ~ 1, 
      pl[,paste0("know_fac_",i, "_post")] %in% incorrect ~ 0
    )
}

# calculate row means and totals
pl$know_post = rowMeans(select(pl,paste0("know_", c(1:5), "_post")), na.rm = T)
pl$know_fac_post = rowSums(select(pl,paste0("know_fac_", c(1:4), "_post")), 
                           na.rm = T)
```

> Political participation

**United States** and **Poland** [only in post-survey]: In the list below, 
select all political activities in which you were involved in the months:

  - Signed a petition 
  - Donated or collected money
  - Shared my thoughts in social media  
  - Attended a political meeting
  - Participated in a protest
  - Contacted the politician             
  - Volunteered for a campaign             
  - Wrote a letter to the media

```{r}
# UNITED STATES
us$ptc_post = sapply(strsplit(us$ptc, ","), length)

# POLAND
pl$ptc_post = rowSums(select(pl, paste0("ptc_", 1:8, "_post")))
```

> Attitude strength

How strong are your views on each of the following issues?	
[1 'not strong at all', 7 'very strong']

**United States**

  - Gun control
  - Immigration
  - Climate
  - Economy 
  
**Poland** 

  - Women's rights
  - Religion and the Church in public life
  - Poland's relations with the EU
  - Economy

```{r}
# UNITED STATES 
us_issues = c("gun", "immigrant", "climate", "econ")

us$att_str_pre = rowMeans(select(us, paste0("att_str_", us_issues, "_pre")))
us$att_str_post = rowMeans(select(us, paste0("att_str_", us_issues, "_post")))

# POLAND
pl$att_str_pre = rowMeans(
  select(pl, paste0("att_str_", 1:4, "_pre")), na.rm = T) # BC: this should be 5 issues according to PAP
pl$att_str_post = rowMeans(
  select(pl, paste0("att_str_", 1:4, "_post")),  na.rm = T)
```

> Attitude importance 

How important is each of the following issues to you personally?
[1 'not at all important', 7 'very important']

**United States**

  - Gun control
  - Immigration
  - Climate
  - Economy 
  
**Poland** 

  - Women's rights
  - Religion and the Church in public life
  - Poland's relations with the EU
  - Economy
  
```{r}
# UNITED STATES 

us$att_imp_pre = rowMeans(select(us, paste0("att_imp_", us_issues, "_pre")))
us$att_imp_post = rowMeans(select(us, paste0("att_imp_", us_issues, "_post")))

# POLAND 

pl$att_imp_pre = rowMeans(
  select(pl, paste0("att_imp_", 1:4, "_pre")), na.rm = T)
pl$att_imp_post = rowMeans(
  select(pl, paste0("att_imp_", 1:4, "_post")),  na.rm = T)
```


> Affective polarization 

    1. *Feeling thermometer:* We'd like you to rate several different groups and 
       individuals using something called a "feeling thermometer". The higher 
       the number, the warmer or more favorable you feel toward the group; the 
       lower the number, the colder or less favorable. Please rate how you feel 
       about the following groups and individuals.	
       [0 'Very cold', 100 'Very warm']
    2. *Negative traits:* To what extent do you agree or disagree with the 
       statement that supporters of ... are stupid.
       [1 'strongly disagree' 2 'strongly agree']
    3. *Understanding:* How much do you understand the perspectives and values 
       of the following groups ("I understand" does not necessarily mean that 
       you agree with them). [1 not at all - 7 very much]

**United States**

  - Supporters of the Democratic Party
  - Supporters of the Republican Party
  - Liberals
  - Conservatives
  - Those with opposite views on gun control
  - Those with opposite views on immigration
  - Those with opposite views on climate change
  - Those with opposite views on the economy
  
**Poland**

  - The party you feel farthest from
  - Supporters of PiS
  - Supporters of SLD
  - Leftist citizens
  - Rightist citizens 
  - Those with opposite views on women's rights
  - Those with opposite views on religion and the church in public life
  - Those with opposite views on Poland's relations with the EU
  - Those with opposite views on the economy
  
```{r}
# UNITED STATES 

# invert all feeling thermometer variables
for(i in names(us)[grepl("ft_", names(us))]){us[,i] = invert(us[,i])}

# identify affective polarization variable according to partisanship
for (i in 1:3){
  
  var = c("ft", "under", "stupid")[i]
  var_party = paste0(var, "_party_op")
  var_ideo = paste0(var, "_ideo_op")
  
  for (w in c("_pre", "_post")){
    
    for (j in 1:2){
     
    newvar = list(var_party, var_ideo)[[j]]
    
    if (i == 1){
    g1 = c(paste0(var, "_dem"), paste0(var, "_lib"))[j]
    g2 = c(paste0(var, "_rep"), paste0(var,"_cons"))[j]
    } else {
    g1 = paste0(var, "_party_opp")
    g2 = paste0(var, "_party_opp")
    }
      
    us[, paste0(newvar, w)] = us[, paste0(g1, w)]
    us[us$party_bin == "Democrat" & !is.na(us$party_bin), paste0(newvar, w)] = 
      us[us$party_bin == "Democrat" & !is.na(us$party_bin), paste0(g2, w)]
    
    }
  
  # dimensions: out-partisans, out-ideologues, out-policy
  us[, paste0(var, w)] = rowMeans(cbind(
    select(us, paste0(var_party, w), paste0(var_ideo, w)), 
    rowMeans(select(us, paste0(var, paste0("_", us_issues), w)), 
             na.rm = T),
    na.rm = T))
  }}

## POLAND

# invert all feeling thermometer variables
for(i in names(pl)[grepl("ft_", names(pl))]){pl[,i] = invert(pl[,i])}

pl_issues = c("women", "rel", "eu", "econ")

# identify affective polarization variable according to partisanship
for (i in 1:3){
  
  var = c("ft", "under", "stupid")[i]
  var_party = paste0(var, "_party_op")
  var_ideo = paste0(var, "_ideo_op")
  
  for (w in c("_pre", "_post")){
    
  if (i %in% c(1,2)){
    
    for (j in 1:2){
     
    newvar = list(var_party, var_ideo)[[j]]
    
    g1 = c(paste0(var, "_sld"), paste0(var, "_lw"))[j]
    g2 = c(paste0(var, "_pis"), paste0(var,"_rw"))[j]
      
    pl[, paste0(newvar, w)] = pl[, paste0(g1, w)]
    pl[pl$party_bin == "Anti" & !is.na(pl$party_bin), paste0(newvar, w)] = 
      pl[pl$party_bin == "Anti" & !is.na(pl$party_bin), paste0(g2, w)]
    
    }
  
  # dimensions: out-partisans, out-ideologues, out-policy
  pl[, paste0(var, w)] = rowMeans(
    
    data.frame(
    # party 
    rowMeans(select(pl, c(paste0(var_party, w), paste0("ft_far", w))), 
             na.rm = T),
    # ideology 
    select(pl, paste0(var_ideo, w)),
    # policy
    rowMeans(select(pl, paste0(var, paste0("_", pl_issues), w)), na.rm = T)),
    na.rm = T)
  } else {
      
  pl[, paste0(var, w)] = rowMeans(cbind(
    select(pl, "stupid_far_pre"), 
    rowMeans(select(pl, paste0(var, paste0("_", pl_issues), w)), na.rm = T)),
    na.rm = T)
    }}}
```

> Attribution of malevolence 

**United States** and **Poland**

To what extent do you agree with the following statements?
[1 'strongly disagree' 7 'strongly agree']

  - I worry that [out-partisans] are deliberately trying to hurt America.
  - [out-partisans] are knowingly sabotaging the country.
  - [out-partisans] don't care about [country]
  - I believe [out-partisans] genuinely want what is best for [country] (-)
  - I trust [out-partisans] to do what they think is best for [country] (-)

```{r}
# UNITED STATES

# invert negatively coded items 
for (i in 4:5){
us[,paste0("malvol_", i, "_pre")] = invert(us[,paste0("malvol_", i, "_pre")])
us[,paste0("malvol_", i, "_post")] = invert(us[,paste0("malvol_", i, "_post")])
}

# calculate row means
us$malvol_pre = rowMeans(select(us, paste0("malvol_", 1:5, "_pre")), na.rm = T)
us$malvol_post = 
  rowMeans(select(us, paste0("malvol_", 1:5, "_post")), na.rm = T)

# POLAND 

# identify malevolence variable according to partisanship
for (i in 1:5){
  for (w in c("_pre", "_post")){
    pl[, paste0("malvol_", i, w)] = pl[, paste0("malvol_gov_", i, w)]
    pl[pl$party_bin == "Pro", paste0("malvol_", i, w)] = 
      pl[pl$party_bin == "Pro", paste0("malvol_op_", i, w)]
}}

# invert negatively coded items 
for (i in 4:5){
pl[,paste0("malvol_", i, "_pre")] = invert(pl[,paste0("malvol_", i, "_pre")])
pl[,paste0("malvol_", i, "_post")] = invert(pl[,paste0("malvol_", i, "_post")])
}

# calculate row means
pl$malvol_pre = rowMeans(select(pl, paste0("malvol_", 1:5, "_pre")), na.rm = T)
pl$malvol_post = 
  rowMeans(select(pl, paste0("malvol_", 1:5, "_post")), na.rm = T)
```

> Lack of support for compromise 

**United States** and **Poland**

Which position most closely reflects your views?
[1 'left position' 7 'right position']

  - Politicians must be faithful to their values, no matter what - 
    Politicians must cooperate with each other to be effective first of all, 
    sometimes at the expense of values
  - Politicians should never compromise their values - Sometimes compromise 
    is necessary when solving important problems
  - I want politicians who stick to their opinions and principles - 
    I want politicians who cooperate with each other
  - Values should never be violated - Principles should never block progress

```{r}
# UNITED STATES

# invert inversely coded scales
for (i in 1:4){
  us[,paste0("comp_", i, "_pre")] = invert(us[,paste0("comp_", i, "_pre")])
  us[,paste0("comp_", i, "_post")] = invert(us[,paste0("comp_", i, "_post")])
}

# calculate row means
us$comp_pre = rowMeans(select(us, paste0("comp_", 1:4, "_pre")), na.rm = T)
us$comp_post = rowMeans(select(us, paste0("comp_", 1:4, "_post")), na.rm = T)

# POLAND 

# invert inversely coded scales
for (i in 1:4){
  pl[,paste0("comp_", i, "_pre")] = invert(pl[,paste0("comp_", i, "_pre")])
  pl[,paste0("comp_", i, "_post")] = invert(pl[,paste0("comp_", i, "_post")])
}

# calculate row means
pl$comp_pre = rowMeans(select(pl, paste0("comp_", 1:4, "_pre")), na.rm = T)
pl$comp_post = rowMeans(select(pl, paste0("comp_", 1:4, "_post")), na.rm = T)
```


> Perceived polarization

How much do you agree or disagree with the following statements:
[1 'Strongly disagree' 7 'Strongly agree']

**United States**

  - Democrats and Republicans hate each other.
  - The differences between Democrats and Republicans are too great 
    to be reconciled.
  - Americans are greatly divided when it comes to the most important values.
  - Polarization in America is greater than ever before.
  
**Poland**

  - Supporters and opponents of the current government in Poland hate each other
  - The differences between the supporters and opponents of the current 
    government are too great to reconcile them
  - Poles are very divided when it comes to the most important values
  - Currently, the polarization of views in Poland is greater than ever before

```{r}
# UNITED STATES
us$perpol_pre = rowMeans(select(us, paste0("perpol_", 1:4, "_pre")), na.rm = T)
us$perpol_post = 
  rowMeans(select(us, paste0("perpol_", 1:4, "_post")), na.rm = T)

# POLAND
pl$perpol_pre = rowMeans(select(pl, paste0("perpol_", 1:4, "_pre")), na.rm = T)
pl$perpol_post = 
  rowMeans(select(pl, paste0("perpol_", 1:4, "_post")), na.rm = T)
```

> Decreased personal well-being 

**United States** and **Poland** (post-survey only): 

  1. *Mental well-being:* We would like to ask you about how you felt
  and about some activities you might have done in the last week. Over the past 
  week, how much have you felt each of the following?
  [1 'Not at all' 7 'To a great extent']

    - Depressed 
    - Anxious 
    - Happy (-)
    - Satisfied with life (-)
    - Optimistic about the future (-)
    - Calm and peaceful (-)
    
  2. *Physical well-being:* We would like to ask you about how you felt and 
  about some activities you might have done in the last week. How many days
  in the last week have you done the following 
  [0 to 7]

    - Had one or more alcoholic beverage 
    - Ordered pizza or other fast food
    - Felt like hitting someone 
    - Gotten into an argument 
    - Exercised (-)

```{r}
# UNITED STATES 

# invert inversely coded items 
for (i in 3:6){
  us[, paste0("well_feel_", i, "_post")] = 
    invert(us[, paste0("well_feel_", i, "_post")])
}

us$well_act_5_post = invert(us$well_act_5_post)

# calculate row means 
us$well_feel_post = 
  rowMeans(select(us, paste0("well_feel_", 1:6, "_post")), na.rm = T)
us$well_act_post = 
  rowMeans(select(us, paste0("well_act_", 1:5, "_post")), na.rm = T)

# POLAND

# invert inversely coded items 
for (i in 3:6){
  pl[, paste0("well_feel_", i, "_post")] = 
    invert(pl[, paste0("well_feel_", i, "_post")])
}

pl$well_act_5_post = invert(pl$well_act_5_post)

# calculate row means 
pl$well_feel_post = 
  rowMeans(select(pl, paste0("well_feel_", 1:6, "_post")), na.rm = T)
pl$well_act_post = 
  rowMeans(select(pl, paste0("well_act_", 1:5, "_post")), na.rm = T)
```

## Generate analysis datasets

Reshape data into long dataset
```{r}
# UNITED STATES
colnames(us) = gsub("_pre", "_w1", names(us))
colnames(us) = gsub("_post", "_w2", names(us))

us_long = long_panel(us, prefix = "_w", 
                     begin = 1, end = 2, label_location = "end")

# POLAND
colnames(pl) = gsub("_pre", "_w1", names(pl))
colnames(pl) = gsub("_post", "_w2", names(pl))

pl_long = long_panel(pl, prefix = "_w", 
                     begin = 1, end = 2, label_location = "end")
```

## Rescale variables

Rescale variables 
```{r}
# To data frame
pl_long = data.frame(pl_long)
us_long = data.frame(us_long)

# Dependent variables between 0 and 100
dvs = c("know", "know_fac", "ptc", "att_str", "att_imp", "ft", "under", 
        "stupid", "malvol", "comp", "perpol", "well_act", "well_feel")

for (var in dvs){
  pl_long[,paste0(var, "_r")] = rescale_100(pl_long[,var])
  us_long[,paste0(var, "_r")] = rescale_100(us_long[,var])
}

# Prior news expo natural logarithm 
pl_long <- pl_long %>%
  mutate(news_log = log(news + 1))

us_long <- us_long %>%
  mutate(news_log = log(news + 1))

# for (var in c("news", "news_like")){
#   pl_long[, paste0(var, "_r")] = pl_long[,var] + 1
#   pl_long[, paste0(var, "_r")] = log(pl_long[, paste0(var, "_r")])
#   pl_long[, paste0(var, "_r")] = rescale_100(pl_long[, paste0(var, "_r")])
# 
#   us_long[, paste0(var, "_r")] = us_long[,var] + 1
#   us_long[, paste0(var, "_r")] = log(us_long[, paste0(var, "_r")])
#   us_long[, paste0(var, "_r")] = rescale_100(us_long[, paste0(var, "_r")])
# }
```

## Store data

Save data
```{r}
write.csv(pl, paste0(datadir, "pl_survey_wide_NEW.csv"))
write.csv(us, paste0(datadir, "us_survey_wide_NEW.csv"))
write.csv(pl_long, paste0(datadir, "pl_survey_long_NEW.csv"))
write.csv(us_long, paste0(datadir, "us_survey_long_NEW.csv"))
```